---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Datas

Firstly, we load and concatenate the dataframes

```{r}
FA_Dice_Array <- read.csv("../../table_results/FA_Dice_Array.csv")
FOD_Dice_Array <- read.csv("../../table_results/FOD_Dice_Array.csv")
Rand_Dice_Array <- read.csv("../../table_results/Rand_Dice_Array.csv")
Entropy_Dice_Array <- read.csv("../../table_results/Entropy_Dice_Array.csv")

Dice_Array = rbind(FA_Dice_Array, FOD_Dice_Array, Rand_Dice_Array, Entropy_Dice_Array)
colnames(Dice_Array) <- c("Patient","Nerve", "Parameter", "Condition", "SD_max","Index","Threshold","SD_init","Method")
```


We then clean the dataframe

```{r}
nrep = length(Dice_Array$Patient)/19
Dice_Array$Condition <- rep(c(c(1,2,3,4), rep(c(1,2,3,4,5), 3)), nrep)

Dice_Array$Condition <- as.factor(Dice_Array$Condition)

Dice_Array$SD_max[Dice_Array$SD_init <= 0.01] = NA
Dice_Array$SD_max[Dice_Array$SD_init <= 0.01] = NA

levels(Dice_Array$Nerve) <- c(levels(Dice_Array$Nerve), c("III","NF","NM","V")) 
Dice_Array$Nerve[Dice_Array$Nerve == 'IIID' | Dice_Array$Nerve == 'IIIG'] <- "III"
Dice_Array$Nerve[Dice_Array$Nerve == 'NFD' | Dice_Array$Nerve == 'NFG'] <- "NF"
Dice_Array$Nerve[Dice_Array$Nerve == 'NMD' | Dice_Array$Nerve == 'NMG'] <- "NM"
Dice_Array$Nerve[Dice_Array$Nerve == 'VD' | Dice_Array$Nerve == 'VG'] <- "V"

```

## SD_Max

We look at the SDmax value wich is an indicator of the filtering performance

### Mean Median and Var of SDmax

```{r}
ag1 <- aggregate( SD_max ~ Method, Dice_Array, mean )
ag1$median <- aggregate( SD_max ~ Method, Dice_Array, median)$SD_max
ag1$var <- aggregate( SD_max ~ Method, Dice_Array, var )$SD_max
colnames(ag1)[2] <- "Mean"
ag1
```
All three non random methods seems better than the random one. FOD seem to be 
the overall best method. However, we do not know how significant the differences
between the entropy and the other methode are.

### Wilcox test

With no assumption on the data distribution, but paired data between methods, 
a Wilcox test semms to be the better option.
```{r}

pairwise.wilcox.test(Dice_Array$SD_max, Dice_Array$Method,
                     p.adjust.method = "BH")
pairwise.wilcox.test(Dice_Array[Dice_Array$Nerve == "Chiasma", ]$SD_max,
                     Dice_Array[Dice_Array$Nerve == "Chiasma", ]$Method,
                     p.adjust.method = "BH")
```

Only the FOD and Random methods seem to have significant difference with the 
Entropy methods

### Linear Models

In order to have a better overview at the effect of each methods, despite other
variables, we will build a set of more and more complex linear model.

```{r}

mod1 = lm(Dice_Array$SD_max ~  Dice_Array$Method)
summary(mod1)
```

```{r}
mod2 = lm(Dice_Array$SD_max ~ Dice_Array$Method + Dice_Array$Nerve)
summary(mod2)
```

```{r}
mod3 = lm(Dice_Array$SD_max ~ Dice_Array$Method + Dice_Array$Parameter)
summary(mod3)
```

```{r}
mod4 = lm(Dice_Array$SD_max ~ + Dice_Array$Method + Dice_Array$Nerve + Dice_Array$Parameter, Dice_Array)
summary(mod4)
```

```{r}
mod5 = lm(Dice_Array$SD_max ~ + Dice_Array$Method + Dice_Array$Nerve + Dice_Array$Parameter + Dice_Array$Condition, Dice_Array)
summary(mod5)
```
### Conclusion on SD_max:

The entropy method seems to bring a significant improvement of SD max other 
the random one (+ 0.07, pval < 2e-16). However, the FOD method is slightly 
better than entropy (+0.015, pval = 0.042). There is no significant difference 
in results between FA and Entropy methods.

## Threshold

We then look at the Threshold value witch is an indicator of the filtering 
robustness. Indeed, if the Threshold for the best SD is conserved, we can
expect to have better a-priory filtering.
```{r}
ag1 <- aggregate( Threshold ~ Method, Dice_Array, mean )
ag2 <- aggregate( Threshold ~ Method, Dice_Array, var )

ag1$Threshold_var <- ag2$Threshold
ag1$Threshold_relative_var <- ag2$Threshold / ag1$Threshold
colnames(ag1)[2] <- "Threshold_Mean"
ag1
```
Both Entropy and FOD seems to have conservative threshold values.
```{r}
library(ggplot2)


Relativ_thresh = Dice_Array$Threshold
Relativ_thresh[Dice_Array$Method =="Entropy"] = Dice_Array[Dice_Array$Method =="Entropy","Threshold"]/mean(Dice_Array[Dice_Array$Method =="Entropy", "Threshold"],na.rm = TRUE)
Relativ_thresh[Dice_Array$Method =="FA"] = Dice_Array[Dice_Array$Method =="FA","Threshold"]/mean(Dice_Array[Dice_Array$Method =="FA","Threshold"],na.rm = TRUE)
Relativ_thresh[Dice_Array$Method =="FOD"] = Dice_Array[Dice_Array$Method =="FOD","Threshold"]/mean(Dice_Array[Dice_Array$Method =="FOD","Threshold"],na.rm = TRUE)

ggplot(Dice_Array[Dice_Array$Method !="Rand",], aes(y=Relativ_thresh[Dice_Array$Method !="Rand"], x=Nerve, fill=Method))+ geom_boxplot()+ggtitle("Comparing threshold range between methodes ") + ylab("Relative Best Tresh (mean = 1)") +ylim(0,4)

```
The Entropy method appear to be far more interesting to chose a filtering threshold
```{r}
library(ggplot2)



ggplot(Dice_Array[Dice_Array$Method !="Rand",], aes(y=Dice_Array$Index[Dice_Array$Method !="Rand"], x=Nerve, fill=Method))+ geom_boxplot()+ggtitle("Comparing Index range between methodes ") + ylab("Index")

```

